Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2021-09-19 paper/paper.tex
update

\section{Discussion and conclusion}
We have introduced a new approach based on tensor network contraction to compute the independence number, independence polynomial, maximal independence polynomial, and enumeration of MIS configurations.
We derived the backward rule for tropical tensor network to bound the search of solution space.
Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
The full code base can be found in ~\cite{GraphTensorNetworks}.
%What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
%The style that we program is called generic programming,

>>>>

\subsubsection{Computing the Hamming distance statistics}

\begin{figure} 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
    \caption{The statistics of Hamming distances between two MIS configurations for a specific three regular graph instance of size $200$.}
    \label{fig:hamming}
\end{figure}

\section{Discussion and conclusion}
We have introduced a new approach based on tensor network contraction to compute the independence number, independence polynomial, maximal independence polynomial, and enumeration of MIS configurations.
We derived the backward rule for tropical tensor network to bound the search of solution space.
Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}.
%What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
%The style that we program is called generic programming,
